Efficient Coalition Formation for Web Services

### 2013-04-07 papers/coalition2-journal-extension/coalition_ext.tex
Changes

Figure \ref{performanceall} depicts the results of optimal
\emph{$\epsilon$-core}, \emph{Depth-1 Convex-Checker},
\emph{Depth-2 Convex-Checker}, \emph{3-Way Satisfaction}
\cite{DBLP:conf/IEEEscc/LimTMB12}, and \emph{2 Player
Non-Cooperative} \cite{DBLP:conf/IEEEscc/KhosravifarABT11} methods
in \emph{one grand community with many web services} scenario. For
\emph{$\epsilon$-core}, we assign $\epsilon$ to 15\% of total
community worth, $\epsilon = 0.15 \times v(C)$, which allows
subsets of the coalition to gain maximum 15\% of $v(C)$. In the
\emph{optimal $\epsilon$-core} method, we capped the coalition
size to 25 web services, since anything more than that would
require analysis with time complexity of $O(2^{n-1})$, making it
impractical to run in our simulations. In the other methods, there
were no cap on size of the community and we had communities of
size 60 web services at some points. The results show that our
\emph{depth-2 convex checker} method is performing better compared
to the other methods and its performance is close to optimal
\emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
and \emph{3-Way Satisfaction} are also performing well.

>>>>

Figure \ref{performanceall} depicts the results of optimal
\emph{$\epsilon$-core}, \emph{Depth-1 Convex-Checker},
\emph{Depth-2 Convex-Checker}, \emph{3-Way Satisfaction}
\cite{DBLP:conf/IEEEscc/LimTMB12}, and \emph{2 Player
Non-Cooperative} \cite{DBLP:conf/IEEEscc/KhosravifarABT11} methods
in \emph{one grand community with many web services} scenario. For
\emph{$\epsilon$-core}, we assign $\epsilon$ to 15\% of total
community worth, $\epsilon = 0.15 \times v(C)$, which allows
subsets of the coalition to gain maximum 15\% of $v(C)$. In the
\emph{optimal $\epsilon$-core} method, we capped the coalition
size to 25 web services, since the method is computationally 
intractable and anything more than that would make it
impractical to run in our simulations. In the other methods, there
were no cap on size of the community and we had communities of
size 60 web services at some points. The results show that our
\emph{depth-2 convex checker} method is performing better compared
to the other methods and its performance is close to optimal
\emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
and \emph{3-Way Satisfaction} are also performing well.
